Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-10-17 paper/1_Initial/manuscript.qmd
minor
added a reference

At the same time, these associations were context-dependent: not all item pairings or bodily domains related equally to mood or somatic symptoms [@murphy2019; @koike2023]. Emerging evidence suggests that interoceptive abilities (e.g., sensitivity, precision and metacognitive insight) may not uniformly predict mental health outcomes and may depend on measurement approach or sample characteristics [**REF PRE_PRINT?**].

@@

# General DiscussionGeneral Discussion

>>>>

At the same time, these associations were context-dependent: not all item pairings or bodily domains related equally to mood or somatic symptoms [@murphy2019; @koike2023]. Emerging evidence suggests that interoceptive abilities (e.g., sensitivity, precision and metacognitive insight) may not uniformly predict mental health outcomes and may depend on measurement approach or sample characteristics [@@banellis2025interoceptive].

@@

# General Discussion
